\section{\mysidestyle Professional\\Experience}

\textbf{Vanderbilt University}, Nashville, TN \vspace{2mm}\\\vspace{1mm}%
\textsl{Graduate Research Assistant} \hfill \textbf{Aug 2016 -- Present}\\
Conducted various computational studies of organic chemistry-based compounds using molecular modeling as well as open-source Python software development. Notable work includes:

\begin{itemize}[itemsep=0.5mm, parsep=2pt]
\item Designed and implemented an extensible ``plug-in'' system for our chemical system building library \pkg{mBuild} allowing for dynamic discovery of plug-ins through the use of the \pkg{setuptools} \pkg{entrypoint} functionality.
\item Continued development of our lab's Python libraries by using software development best practices such as unit testing, collaborative code review, continuous integration, object-oriented design patterns, fork and pull request model for code contributions, and input sanitization 
\item Became one of the lead software developers of the lab's open-source Python libraries \url{https://github.com/mosdef-hub}, now involved in a national grant involving 7 other universities.
\item Managed and instructed the simulation of over \num{36000} chemical systems, performed time-series and statistical analysis of data from these systems to use partly as testing/training data of a random forest regression model from \pkg{sklearn}, producing a predictive model linking chemical features to tribological properties.
\item Mentored undergraduate and high school students year-round in molecular simulation, data analysis, and scientific software development best practices.
\item Maintained lab computational equipment, including a 14 node computing cluster.
\item Ensured cluster uptime by performing maintenance
  %Taught version control, software development using Python, data analysis, and interacting with the UNIX shell.
  %Aided students in all aspects of molecular simulation, including award winning poster presentations.
\end{itemize}


\textbf{Vanderbilt University}, Nashville, TN \vspace{2mm}\\\vspace{1mm}%
\textsl{Graduate Teaching Assistant} \hfill \textbf{Aug 2016 -- Dec 2019}\\
Developed course-work and lecture material for a 3\textsuperscript{rd} year molecular simulation course as well as a 1\textsuperscript{st} year engineering computation course.
Created lessons utilizing Jupyter Notebooks, GitHub Classroom, teaching version control and Python to students with little to no experience of programming concepts.
Also performed teaching-assistant duties for a 3\textsuperscript{rd} year mechanical engineering lab, as well as an additional 1\textsuperscript{st} year engineering course.

\textbf{Clemson University}, Clemson, SC \vspace{2mm}\\\vspace{1mm}%
\textsl{Tutor} \hfill \textbf{Aug 2013 -- May 2016}\\
Provided academic tutoring to 500 first year science and engineering students as part of the Residents in Science and Engineering (RiSE) Living-Learning Community (LLC) (\url{https://1n.pm/rise}).
Led general chemistry study sessions for exam preparation.
Mentored minority students through a program offered by the RiSE LLC.